Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
Aaro's asine

@@

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        select(var.BP, var.CL)

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame %>%
        select(-contains("virus"))

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
		normalization = "NONE",
		random_effects = paste0(var.BP, collapse = ","),
             fixed_effects = paste0(var.CL, collapse = ","), 
             cores = detectCores())

>>>>

```{r fit asine}
source("fit_asine.R")
source("taxa_names_functions.R")
```

```{r maaslin}
maaslin <- read.table("maaslin1/maaslin/maaslin.txt", header=TRUE, sep='\t')

maaslin %>% filter(Q.value < 0.05)
```

@@

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        tibble::rownames_to_column("ids") %>%
        tibble::column_to_rownames("ids") %>%
        select(var.BP, var.CL)

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame

    maaslin <- Maaslin2(maaslin.abund %>% select(g_Sutterella, g_Adlercreutzia, g_Anaerotruncus),
                        maaslin.pheno,
                        "maaslin2_example_output",
                        transform = "AST",
                        normalization = "NONE",
                        fixed_effects = paste0(var.CL, collapse = ","),
                        random_effects = paste0(var.BP, collapse = ","))

    random_formula = as.formula("expr ~ (1 | MAP) + (1 | SYSTM) + (1 | DIASM) + (1 | PULSEPRESSURE) + (1 | HYPERTENSION)")
    formula = as.formula("expr ~  BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09")

    formula2 <-
                    paste(
                        '. ~', 
                        paste(all.vars(formula)[-1], collapse = ' + '), 
                        '.', 
                        sep = ' + ')

    formula2

    update(random_formula, formula2)

    maaslin.pheno %>% head(n=1)

    stats::glm(BL_AGE ~ SEX + (1|MAP), family = stats::gaussian, data = meta(pseq.genus.core))

    maaslin$results %>% head(n=1)

    maaslin.abund[1:10,1:10]
    maaslin.pheno[1:10,1:10]

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
             normalization = "NONE",
             random_effects = paste0(var.BP, collapse = ","),
             fixed_effects = paste0(var.CL[1:3], collapse = ","), 
             cores = detectCores())
